---
title: "10-import"
output: html_document
---


# 1. Describe the data and the problem

In Kaggle, I found a data set the contains every data from pitch thrown in a Major League Baseball game from 2015-2018.  Each pitch has a measurement for velocity, horizontal break, vertical break, the pitch result, and much more. I would like to analyze what elements of a pitch produce what results, with what frequency.

# 2. Read in and check data

Running in the necessary libraries:
```{r libararies}
library(tidyverse)
library(janitor)
library(assertr)
library(ggplot2)
library(readr)
```


Reading in the data from the csv's:
```{r import}
pitches <- read_csv("mlb-pitch-data-20152018/pitches.csv")
atbats <- read_csv("mlb-pitch-data-20152018/atbats.csv")
player_names <- read_csv("mlb-pitch-data-20152018/player_names.csv")
```







```{r}
IDpitches <- pitches %>% 
  full_join(atbats, by = "ab_id") %>% 
  full_join(player_names, by = c("pitcher_id" = "id")) %>% 
  full_join(player_names, by = c("batter_id" = "id"))

head(IDpitches)
```

