---
title: "20-exploration"
output: html_document
---

# 2 cont. check the data

There are no identifiers for players in the "pitchers" table.  Joining "pitchers" with the "atbats" data which has player ID's, then joining the "player_names" table which links ID's to names:
```{r joins}
IDpitches <- pitches %>% 
  full_join(atbats, by = "ab_id") %>% 
  full_join(player_names, by = c("pitcher_id" = "id")) %>% 
  full_join(player_names, by = c("batter_id" = "id")) %>% 
  full_join(games, by = "g_id")

head(IDpitches)
```


Exmaining the data:
```{r examine}
str(IDpitches)
summary(IDpitches)
```
The structure of the columns looks good, but there is a lot of dirty data.  I don't think anyone threw a pitch 33 mph in a game, and I'm certain the range of vertical break from -70 to 33 is unrealistic.  Also, the data is littered with NA's


First, removing the NA's:
```{r remove NA}
IDpitchesC <- IDpitches %>% 
  filter(!is.na(start_speed), !is.na(spin_rate), !is.na(pfx_x), !is.na(pfx_z), !is.na(code))

summary(IDpitchesC)
```
This has removed all the NA's from the columns of interest.


Let's look at the results of the pitches:
```{r pitch results tabyl}
tabyl(IDpitchesC$code)
```
We only care about competitive pitches, so let's remove any intentional ball ("I") and pitchout ("P", "Q", "R")
```{r filtering pitches}
IDpitchesC <- IDpitchesC %>% 
  filter(code != c("I", "P", "Q", "R"))
```


Let's check the bounds of a few columns:
```{r assert bounds}
IDpitchesC %>% 
  assert(within_bounds(50, 110), start_speed) %>%
  assert(within_bounds(800, 3600), spin_rate) %>%
  assert(within_bounds(-18, 18), pfx_x) %>%
  assert(within_bounds(-18, 18), pfx_z)
```
There are still pitches with measurements that must be innacurate.


Removing bad readings for certain columns:
```{r filter out bad reads}
IDpitchesC <- IDpitchesC %>% 
  filter(start_speed >= 60, spin_rate >= 800, spin_rate <= 3600, pfx_x >= -18, pfx_x <= 18, pfx_z >= -18, pfx_z <= 18)
```
This dataframe passes the assertr tests above.


The data looks good, let's remove unnecessary columns and rename some of them:
```{r select}
IDpitchesC <- IDpitchesC %>% 
  select(date, p_last = last_name.x, p_first = first_name.x, pitch_type, velo = start_speed, spin_rate, break_x = pfx_x, break_z = pfx_z, result = code, b_last = last_name.y, b_first = first_name.y,)
```






