---
title: "30-feature-engineering"
output: html_document
---
# 4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

##In order to understand each pitch better, let's provide some context, by finding the standard score for velo, spin_rate, break_x, & break_z for each pitch.
```{r standardized measures}
scale <- function(x) round((x - mean(x))/ sd(x), digits = 3)

calc_by_pitch_type <- function(df, vars) {
  df %>% 
    group_by(pitch_type, p_throws) %>% 
    mutate_at(vars, list(std = scale)) %>% 
    ungroup()
}

IDpitchesLite %>% 
  calc_by_pitch_type(c("velo", "spin_rate", "break_x", "break_z"))
```


##Creating columns for the avergae velo, spin_rate, break_x, & break_z of each pitch type by pitchers of that hand:
```{r avg by L/R}
scale2 <- function(x) round((mean(x)), digits = 3)

avg_by_pitch_type_hand <- function(df, vars) {
  df %>% 
    group_by(pitch_type, p_throws) %>% 
    mutate_at(vars, list(avg = scale2)) %>% 
    ungroup()
}

IDpitchesLite %>% 
  avg_by_pitch_type_hand(c("velo", "spin_rate", "break_x", "break_z"))
```

##Creating columns for the maximum velo, spin_rate, break_x, & break_z of each pitch type by an individual pitcher:
```{r personal max}
scale3 <- function(x) round((max(x)), digits = 3)

max_by_pitch_type_pitcher <- function(df, vars) {
  df %>% 
    group_by(pitch_type, pitcher_id) %>% 
    mutate_at(vars, list(max = scale3)) %>% 
    ungroup()
}

IDpitchesLite %>% 
  max_by_pitch_type_pitcher(c("velo", "spin_rate", "break_x", "break_z"))
```


##There still seems to be a lot of funny looking data.  Let's standardize our pitch measures relative to that pitcher's personal distribution. This will make it easier to identify outliers as possible bad readings:
```{r standarize by pitcher pitch type}
scale4 <- function(x) round((x - mean(x))/ sd(x), digits = 3)

calc_by_pitcher_pitch_type <- function(df, vars) {
  df %>% 
    group_by(pitch_type, pitcher_id) %>% 
    mutate_at(vars, list(pitcher_std = scale4)) %>% 
    ungroup()
}

IDpitchesLite %>% 
  calc_by_pitcher_pitch_type(c("velo", "spin_rate", "break_x", "break_z"))
```

