---
title: "30-feature-engineering"
output: html_document
---
# 4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

##Finding the standard score for velo, spin_rate, break_x, & break_z for each pitch.
```{r}
scale <- function(x) (x - mean(x))/ sd(x)

calc_by_pitch_type <- function(df, vars) {
  df %>% 
    group_by(pitch_type) %>% 
    mutate_at(vars, list(std_type = scale)) %>% 
    ungroup()
}

IDpitchesLite %>% 
  calc_by_pitch_type(c("velo", "spin_rate", "break_x", "break_z"))
```


##Creating columns for the avergae velo, spin_rate, break_x, & break_z of each pitch type by pitchers of that hand:
```{r}
scale2 <- function(x) (mean(x))

avg_by_pitch_type_hand <- function(df, vars) {
  df %>% 
    group_by(pitch_type, p_throws) %>% 
    mutate_at(vars, list(avg = scale2)) %>% 
    ungroup()
}

IDpitchesLite %>% 
  avg_by_pitch_type_hand(c("velo", "spin_rate", "break_x", "break_z"))
```

##Creating columns for the maximum velo, spin_rate, break_x, & break_z of each pitch type by an individual pitcher:
```{r}
scale3 <- function(x) (max(x))

max_by_pitch_type_pitcher <- function(df, vars) {
  df %>% 
    group_by(pitch_type, pitcher_id) %>% 
    mutate_at(vars, list(max = scale3)) %>% 
    ungroup()
}

IDpitchesLite %>% 
  max_by_pitch_type_pitcher(c("velo", "spin_rate", "break_x", "break_z"))
```


##Creating columns for the minimum velo, spin_rate, break_x, & break_z of each pitch type by an individual pitcher:
```{r}
scale4 <- function(x) (min(x))

min_by_pitch_type_pitcher <- function(df, vars) {
  df %>% 
    group_by(pitch_type, pitcher_id) %>% 
    mutate_at(vars, list(min = scale4)) %>% 
    ungroup()
}

IDpitchesLite %>% 
  min_by_pitch_type_pitcher(c("velo", "spin_rate", "break_x", "break_z"))
```

