---
title: "assign4"
output: html_notebook
---

#Import
```{r import}
library(tidyverse)
library(lubridate)
library(stringr)
library(glue)
library(RVerbalExpressions)
```


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r first of the month}
first_day_of_months <- floor_date(today(), unit = "year") + months(0:11)
first_day_of_months

```


Write a function that given your birthday (as a date), returns how old you are in years.
```{r age}
age <- function(x) {
  as.period(today() - (ymd(x))) %/% years(1)
}

age(ymd("1989-12-01"))
```


Write a function that given your birthday, returns the day of the week you were born on.
```{r day of week DOB}
MTW_dob <- function(x){
  wday(ymd(x), label = TRUE)
}

MTW_dob("1989-12-01")
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)
```{r seven letter words}
#regular expression
words <- stringr::words

str_view(words, ".......", match = TRUE)

#verbal expression
seven_letter_words <- rx() %>% 
  rx_start_of_line() %>%
  rx_word_char() %>%
  rx_repeat_previous(7) %>%
  rx_anything() %>% 
  print()
  
str_view(words, seven_letter_words, match = TRUE)
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)
```{r no vowels}
#regular expression
words[str_detect(words, "^[^aeiou]+$")]

#verbal expression
all_consonants <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but("aeiou") %>% 
  rx_end_of_line()

words[str_detect(words, all_consonants)]

```


Empirically verify the rule “i before e except after c”.
```{r}
#regular expression
words[str_detect(words, "[^c]ei")]

#verbal expression
ei <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything() %>% 
  rx_anything_but("c") %>% 
  rx_find("ei")

words[str_detect(words, ei)]

#4 words from the set break the rule
```


Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.
```{r}
#regular expression
grepl("^\\d{3}[-\\.]\\d{3}[-\\.]\\d{4}$", "217-377-2867")

#verbal expression
telrx <- rx() %>% 
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line()

grepl(telrx, "217-377-2867")

```




# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

